Report and Figures

### 2016-11-11 figs.Rmd
increased label size in detroit

g +
  geom_point(aes(x = long, y = lat), data = labels, size = 6, pch=21, color = 'black', fill = 'white', alpha = .6) + 
  geom_text(aes(x = long, y = lat, label = label), 
                  data = labels, 
                  size = 4, fontface = 'bold')

out_dir <- paste0('figs/cluster_map_Detroit.pdf')

>>>>

g +
  geom_point(aes(x = long, y = lat), data = labels, size = 9, pch=21, color = 'black', fill = 'white', alpha = .6) + 
  geom_text(aes(x = long, y = lat, label = label), 
                  data = labels, 
                  size = 7, fontface = 'bold')

out_dir <- paste0('figs/cluster_map_Detroit_labeled.pdf')
